Lattice model

### 2017-04-10 oopsla17/lattice-model.tex
Add equivalence from the connecting lemma
Fix Exact set definition

\todo{On the following, add some intutition first- what is this and
  what is it for?}
\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{align*}
    \mathit{ES}_{P,0} & = \{ p \in P \mid \forall \i.\ \pi_i(p) \in \interv{-1}{1}{} \} \\
    \mathit{ES}_{P,d} & =
      \{ p \in P \mid \forall i.\
      p_i \notin [-1,1] \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{adjacent}(p,i) \}
  \end{align*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then
  $\bigcup_{1 \leq d \leq D} \mathit{ES}_{P,d}$, where $D$ is the maximum origin
  distance in $P$.
\end{defn}

\begin{lem}{(\emph{Connecting})}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ defines a superposition of hyper-rectangles each of which crosses
      the extended origin;
    \item $P$ is the same as its exact set $\mathit{ES}_P$;
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ is a subset of \region{N}.
  \end{enumerate}
\end{lem}

>>>>

\todo{On the following, add some intutition first- what is this and
  what is it for?}
\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional subscripts $S$ is defined below:
%
  \begin{align*}
    \mathit{ES}_{S,0} = &
      \{ s \in S \mid \forall \i.\ \pi_i(s) \in \{\{-1\}, \{0\}, \{1\}\} \} \\
    \mathit{ES}_{S,d} = &
      \{ s \in S \mid \forall i.\
      \pi_i(s) \notin \{\{-1\}, \{0\}, \{1\}\} \implies
      \exists s' \in \mathit{ES}_{S,d-1}.\ s' =
         \mathit{adjacent}(s,i) \}
  \end{align*}
%
  The overall \emph{exact set}, $\mathit{ES}_S$ is then
  $\bigcup_{0 \leq d \leq D} \mathit{ES}_{S,d}$, where $D$ is the maximum origin
  distance in $S$.
\end{defn}

\begin{lem}{(\emph{Connecting})}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ is the same as its exact set $\mathit{ES}_P$;
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ is a subset of \region{N}.
  \end{enumerate}
\end{lem}
